---
title: "Gapminder Analysis"
author: "Dave Talarico"
date: "10/14/2019"
output: 
  html_document:
    keep_md: yes
    fig_caption: yes
    toc: yes
---


# Introduction

Here is my first rmd document

# Let's embed some r code

We'll write an R chunk that loads tidyverse package then reads in the Gapminder data set from the data subdirectory of the project

CMD + OPT + i to insert r chunk
highlight string then type quotes to add quotes at start and end
cmd shit K knitr shortcut
toc created via our hashtag headings listed (toc depth = num of #)
```{r message=FALSE}
library(tidyverse)
gm <- read_csv("Data/gapminder.csv")
```

# Investigate gm data

Let's take a look
```{r}
head(gm)
```

# Our First Plot
showing gdp per capita on X & life expectancy on Y
```{r fig.cap = "Life Expectancy V. GDP"}
gm %>% 
  ggplot(aes(x = gdpPercap, y = lifeExp)) +
  geom_point()
```

# A Better Plot

```{r fig.cap = "Life Expectancy V. GDP", fig.width= 10, fig.height=10}
gm %>% 
  ggplot(aes(x = gdpPercap, y = lifeExp)) +
  geom_point(aes(color = continent)) +
  scale_x_log10()
```

# Possible chunk options

Options include:
- echo (defaults TRUE) whether to include code in output
- results 
  - hide will hide results
  - hold holds all results until end of r chunk
- include(defaults TRUE) if FALSE code wont be run
- fig.width, fig.height set dimensions in output
- cache (deafults FALSE) if TRUE saves result from R chunk

# Table in rMarkdown

See some data using head
```{r}
head(gm)
```

now head function into a nicely formatted table
```{r}
library(knitr)
kable(head(gm))
```

If you like tables, look into **gt** table package

kniting as pdf

NOT WORKING
```{r}
#library(tinytex)

```

